---
title: "ST301_A1_Report"
author: "S16_806"
date: "10/12/2020"
output:
  word_document: default
  pdf_document: default
---

Introductin

A real estate agent wants to develop a model to predict the sale price of a house using data collected from 5575 sold houses. we assumes that the following variables which may useful in predicting the sale price of a given house.
1. soldPrice - sold price of house
2. sqftLiving - square footage of living area
3. sqftLand - square footage of land
4. sqftAbove - square footage of area above ground
5. sqftBasement - square footage of basement
6. numBedRooms - number of bed rooms
7. numBathRooms - number of bath rooms
8. numFloors - number of ﬂoors
9. builtYear - year of construction
10. grade - construction quality ranked from 1 to 4 where 1 is the lowest grade
11. waterFront- whether the house has a waterfront (1) or not (0)
12. condition - condition of the house (Excellent, Good, Average)

Exploratory Analysis 

```{r data}
housePrice=read.csv("F:\\study_note\\3rd year\\ST301\\A\\housePrice.csv")
```

```{r variablse}
variable.names(housePrice)
```
Forward Selection Method
Iteration 1

```{r summary1}
summary(lm(soldPrice ~ sqftLiving, data = housePrice))$adj.r.squared

```
```{r summary2}
summary(lm(soldPrice ~ sqftLand, data = housePrice))$adj.r.squared
```
```{r summary3}
summary(lm(soldPrice ~ sqftAbove, data = housePrice))$adj.r.squared
```
```{r summary4}
summary(lm(soldPrice ~ sqftBasement, data = housePrice))$adj.r.squared
```

```{r summary5}
summary(lm(soldPrice ~ numBedRooms, data = housePrice))$adj.r.squared
```
```{r summary6}
summary(lm(soldPrice ~ numBathRooms, data = housePrice))$adj.r.squared
```
```{r summary7}
summary(lm(soldPrice ~ numFloors, data = housePrice))$adj.r.squared
```
```{r summary8}
summary(lm(soldPrice ~ builtYear, data = housePrice))$adj.r.squared
```
```{r summary9}
summary(lm(soldPrice ~ grade, data = housePrice))$adj.r.squared
```
```{r summary10}
summary(lm(soldPrice ~ waterFront, data = housePrice))$adj.r.squared
```
```{r summary11}
summary(lm(soldPrice ~ condition, data = housePrice))$adj.r.squared
```
we can add sqftLiving 
Iteration 2

```{r summary12}
summary(lm(soldPrice ~ sqftLiving+sqftLand, data = housePrice))$adj.r.squared
```
```{r summary13}
summary(lm(soldPrice ~ sqftLiving+sqftAbove, data = housePrice))$adj.r.squared
```
```{r summary14}
summary(lm(soldPrice ~ sqftLiving+sqftBasement, data = housePrice))$adj.r.squared
```
```{r summary15}
summary(lm(soldPrice ~ sqftLiving+numBedRooms, data = housePrice))$adj.r.squared
```
```{r summary16}
summary(lm(soldPrice ~ sqftLiving+numBathRooms, data = housePrice))$adj.r.squared
```
```{r summary17}
summary(lm(soldPrice ~ sqftLiving+numFloors, data = housePrice))$adj.r.squared
```
```{r summary18}
summary(lm(soldPrice ~ sqftLiving+builtYear, data = housePrice))$adj.r.squared
```
```{r summary19}
summary(lm(soldPrice ~ sqftLiving+grade, data = housePrice))$adj.r.squared
```
```{r summary20}
summary(lm(soldPrice ~ sqftLiving+waterFront, data = housePrice))$adj.r.squared
```
```{r summary21}
summary(lm(soldPrice ~ sqftLiving+condition, data = housePrice))$adj.r.squared
```

we can add builtYear
Iteration 3

```{r summary22}
summary(lm(soldPrice ~ sqftLiving+builtYear+sqftLand, data = housePrice))$adj.r.squared
```
```{r summary23}
summary(lm(soldPrice ~ sqftLiving+builtYear+sqftAbove, data = housePrice))$adj.r.squared
```
```{r summary24}
summary(lm(soldPrice ~ sqftLiving+builtYear+sqftBasement, data = housePrice))$adj.r.squared
```
```{r summary25}
summary(lm(soldPrice ~ sqftLiving+builtYear+numBedRooms, data = housePrice))$adj.r.squared
```
```{r summary26}
summary(lm(soldPrice ~ sqftLiving+builtYear+numBathRooms, data = housePrice))$adj.r.squared
```
```{r summary27}
summary(lm(soldPrice ~ sqftLiving++builtYear+numFloors, data = housePrice))$adj.r.squared
```
```{r summary28}
summary(lm(soldPrice ~ sqftLiving++builtYear+grade, data = housePrice))$adj.r.squared
```
```{r summary29}
summary(lm(soldPrice ~ sqftLiving+builtYear+waterFront, data = housePrice))$adj.r.squared
```
```{r summary30}
summary(lm(soldPrice ~ sqftLiving+builtYear+condition, data = housePrice))$adj.r.squared
```

we can add grade
Iteration 4

```{r summary31}
summary(lm(soldPrice ~ sqftLiving+builtYear+grade+sqftLand, data = housePrice))$adj.r.squared
```
```{r summary32}
summary(lm(soldPrice ~ sqftLiving+builtYear+grade+sqftAbove, data = housePrice))$adj.r.squared
```
```{r summary33}
summary(lm(soldPrice ~ sqftLiving+builtYear+grade+sqftBasement, data = housePrice))$adj.r.squared
```
```{r summary34}
summary(lm(soldPrice ~ sqftLiving+builtYear+grade+numBedRooms, data = housePrice))$adj.r.squared
```
```{r summary35}
summary(lm(soldPrice ~ sqftLiving+builtYear+grade+numBathRooms, data = housePrice))$adj.r.squared
```
```{r summary36}
summary(lm(soldPrice ~ sqftLiving+builtYear+grade+numFloors, data = housePrice))$adj.r.squared
```
```{r summary37}
summary(lm(soldPrice ~ sqftLiving+builtYear+grade+waterFront, data = housePrice))$adj.r.squared
```
```{r summary38}
summary(lm(soldPrice ~ sqftLiving+builtYear+grade+condition, data = housePrice))$adj.r.squared
```
we can add waterFront
Iteration 5

```{r summary39}
summary(lm(soldPrice ~ sqftLiving+builtYear+grade+waterFront+sqftLand, data = housePrice))$adj.r.squared
```
```{r summary40}
summary(lm(soldPrice ~ sqftLiving+builtYear+grade+waterFront+sqftAbove, data = housePrice))$adj.r.squared
```
```{r summary41}
summary(lm(soldPrice ~ sqftLiving+builtYear+grade+waterFront+sqftBasement, data = housePrice))$adj.r.squared
```
```{r summary42}
summary(lm(soldPrice ~ sqftLiving+builtYear+grade+waterFront+numBedRooms, data = housePrice))$adj.r.squared
```
```{r summary43}
summary(lm(soldPrice ~ sqftLiving+builtYear+grade+waterFront+numBathRooms, data = housePrice))$adj.r.squared
```
```{r summary44}
summary(lm(soldPrice ~ sqftLiving+builtYear+grade+waterFront+numFloors, data = housePrice))$adj.r.squared
```
```{r summary45}
summary(lm(soldPrice ~ sqftLiving+builtYear+grade+waterFront+condition, data = housePrice))$adj.r.squared
```
we can add numBedRooms
Iteration 6

```{r summary46}
summary(lm(soldPrice ~ sqftLiving+builtYear+grade+waterFront+numBedRooms+sqftLand, data = housePrice))$adj.r.squared
```
```{r summary47}
summary(lm(soldPrice ~ sqftLiving+builtYear+grade+waterFront+numBedRooms+sqftAbove, data = housePrice))$adj.r.squared
```
```{r summary48}
summary(lm(soldPrice ~ sqftLiving+builtYear+grade+waterFront+numBedRooms+sqftBasement, data = housePrice))$adj.r.squared
```
```{r summary49}
summary(lm(soldPrice ~ sqftLiving+builtYear+grade+waterFront+numBedRooms+numBathRooms, data = housePrice))$adj.r.squared
```
```{r summary50}
summary(lm(soldPrice ~ sqftLiving+builtYear+grade+waterFront+numBedRooms+numFloors, data = housePrice))$adj.r.squared
```
```{r summary51}
summary(lm(soldPrice ~ sqftLiving+builtYear+grade+waterFront+numBedRooms+condition, data = housePrice))$adj.r.squared
```
we can add numFloors
Iteration 7

```{r summary52}
summary(lm(soldPrice ~ sqftLiving+builtYear+grade+waterFront+numBedRooms+numFloors+sqftLand, data = housePrice))$adj.r.squared
```

```{r summary53}
summary(lm(soldPrice ~ sqftLiving+builtYear+grade+waterFront+numBedRooms+numFloors+sqftAbove, data = housePrice))$adj.r.squared
```

```{r summary54}
summary(lm(soldPrice ~ sqftLiving+builtYear+grade+waterFront+numBedRooms+numFloors+sqftBasement, data = housePrice))$adj.r.squared
```

```{r summary55}
summary(lm(soldPrice ~ sqftLiving+builtYear+grade+waterFront+numBedRooms+numFloors+numBathRooms, data = housePrice))$adj.r.squared
```

```{r summary56}
summary(lm(soldPrice ~ sqftLiving+builtYear+grade+waterFront+numBedRooms+numFloors+condition, data = housePrice))$adj.r.squared
```
we can add numBathRooms
Iteration 8


```{r summary57}
summary(lm(soldPrice ~ sqftLiving+builtYear+grade+waterFront+numBedRooms+numFloors+numBathRooms+sqftLand, data = housePrice))$adj.r.squared
```

```{r summary58}
summary(lm(soldPrice ~ sqftLiving+builtYear+grade+waterFront+numBedRooms+numFloors+numBathRooms+sqftAbove, data = housePrice))$adj.r.squared
```

```{r summary59}
summary(lm(soldPrice ~ sqftLiving+builtYear+grade+waterFront+numBedRooms+numFloors+numBathRooms+sqftBasement, data = housePrice))$adj.r.squared
```

```{r summary60}
summary(lm(soldPrice ~ sqftLiving+builtYear+grade+waterFront+numBedRooms+numFloors+numBathRooms+condition, data = housePrice))$adj.r.squared
```
we can add sqft
Iteration 9


```{r summary61}
summary(lm(soldPrice ~ sqftLiving+builtYear+grade+waterFront+numBedRooms+numFloors+numBathRooms+sqftAbove+sqftLand, data = housePrice))$adj.r.squared
```

```{r summary62}
summary(lm(soldPrice ~ sqftLiving+builtYear+grade+waterFront+numBedRooms+numFloors+numBathRooms+sqftAbove+sqftBasement, data = housePrice))$adj.r.squared
```

```{r summary63}
summary(lm(soldPrice ~ sqftLiving+builtYear+grade+waterFront+numBedRooms+numFloors+numBathRooms+sqftAbove+condition, data = housePrice))$adj.r.squared
```
Iteration 10

```{r summary64}
summary(lm(soldPrice ~ sqftLiving+builtYear+grade+waterFront+numBedRooms+numFloors+numBathRooms+sqftAbove+sqftLand+sqftBasement, data = housePrice))$adj.r.squared
```
```{r summary65}
summary(lm(soldPrice ~ sqftLiving+builtYear+grade+waterFront+numBedRooms+numFloors+numBathRooms+sqftAbove+sqftLand+condition, data = housePrice))$adj.r.squared
```
Iteration 11

```{r summary66}
summary(lm(soldPrice ~ sqftLiving+builtYear+grade+waterFront+numBedRooms+numFloors+numBathRooms+sqftAbove+sqftLand+condition+sqftBasement, data = housePrice))$adj.r.squared
```
Model Fitting 

We can take as a final fitted model from iteration 11.

Discussion and Conclusion

we can plot this model what we selected(below).summary 65 and summary 66 are got same value  0.5952841.
if we go to predicting sales prices, All coefficient of the model are non negative then we can say that predicting values are always increasing from some unit.

```{r plot}
plot(c(1,2,3,4,5,6,7,8,9,10,11),c(0.4940643,0.5205632,0.5485533,0.5679138,0.5829823,0.5893767,0.5924343,0.5942811,0.5949049,0.5952841,0.5952841))
```

